---
title: "Extra Analyses"
output:
  pdf_document: default
  html_document: default
date: "2025-03-14"
---


```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
library(fastDummies)
library(RColorBrewer)
library(scales)
library(lfe)
library(haven)
library(readxl)
library(readr)
library(dplyr)
library(ivreg)
library(gridExtra)
library(tinytex)
library(synthdid)
library(did)
library(tidyverse)
```


### 1. Load data, preprocess

```{r, echo=FALSE, warning=FALSE}
path <- file.path("D:", "Groups", "YSPH-HPM-Ndumele", "Networks", "Dohyun",
                  "medicaid_privatization_exp")

save_path <- file.path("D:", "Groups", "YSPH-HPM-Ndumele", "Networks", "Dohyun",
                       "medicaid_privatization_exp", "Output")

new_merged_data <- readRDS(paste0(path, "/Temp/new_merged_panel_inflation_adj.rds"))


jumps <- readRDS(paste0(path, "/Temp/jumps.rds"))
jumps <- jumps %>%
  rename(pct_in_comp_mco_jump = pct_in_comp_mco)

# Reformat state names
new_merged_data$state <- tolower(new_merged_data$state)
jumps$state <- tolower(jumps$state)

# Remove Puerto Rico
new_merged_data <- new_merged_data %>%
  filter(state != "puerto rico") %>%
  filter(year %in% 1991:2022)

# Merge 1991-2022 panel with mandate data
main_data <- left_join(new_merged_data, jumps, by = "state")

# Categorize states into treatment groups
never_treated_states <- c("alabama", "alaska", "maine",
                          "montana", "south dakota", "wyoming",
                          "arkansas", "idaho")

clean_treated_states <- c("arizona", "connecticut", "delaware", "hawaii",
                          "new jersey", "north carolina", "new mexico",
                          "oregon", "rhode island", "tennessee", "georgia",
                          "iowa", "nebraska", "new hampshire", "nevada",
                          "washington")

gradually_treated_states <- c("indiana", "oklahoma", "massachusetts",
                              "florida", "kentucky", "louisiana",
                              "mississippi", "north dakota", "california",
                              "colorado", "district of columbia", "kansas",
                              "missouri", "new york",
                              "pennsylvania", "south carolina",
                              "texas", "virginia", "west virginia",
                              "vermont")
always_treated <- c("utah", "maryland", "michigan",
                    "illinois", "minnesota", "ohio",
                    "wisconsin")

# Create variable for treatment categories
main_data <- main_data %>%
  mutate(category = ifelse(state %in% clean_treated_states,
                           "clean treated",
                           ifelse(state %in% gradually_treated_states,
                                  "gradually treated",
                                  ifelse(state %in% always_treated,
                                         "always treated", 
                                         "never treated"))))

# Create variable for medicaid spending per capita and fill treatment years 
# for never treated states with Inf
main_data <- main_data %>%
  mutate(all_medicaid_spending_per_cap = `total medicaid (mt + at)` / total_med_enr,
         log_all_medicaid_spending_per_cap = log(all_medicaid_spending_per_cap)) %>%
  mutate(treatment_year = case_when(
    category == "clean treated" ~ treatment_year,
    category == "gradually treated" ~ treatment_year,
    category == "never treated" ~ Inf,
    category == "always treated" ~ 1991
  ))

# re-define treatment year
# Standard: the first year a state's Comp MMC is >= 10\% of total enrollment 
main_data <- main_data %>%
  mutate(treatment_year = case_when(
    ## never treated states
    state == "alabama" ~ Inf,
    state == "alaska" ~ Inf,
    state == "maine" ~ Inf,
    state == "montana" ~ Inf,
    state == "south dakota" ~ Inf,
    state == "wyoming" ~ Inf,
    state == "arkansas" ~ Inf,
    state == "idaho" ~ Inf,
    
    ## clean treated states
    state == "arizona" ~ 1996,
    state == "connecticut" ~ 1996, # turn-off in 2012
    state == "delaware" ~ 1996,
    state == "hawaii" ~ 1995,
    state == "new jersey" ~ 1995, 
    state == "north carolina" ~ 2021,
    state == "new mexico" ~ 1997,
    state == "oregon" ~ 1994,
    state == "rhode island" ~ 1995,
    state == "tennessee" ~ 1994,
    state == "georgia" ~ 2006,
    state == "iowa" ~ 2016, # weird; need check
    state == "nebraska" ~ 1996,
    state == "new hampshire" ~ 2014,
    state == "washington" ~ 1994,
    state == "nevada" ~ 1998,
    
    ## gradually treated states
    state == "indiana" ~ 1995, # or 1996
    state == "oklahoma" ~ 1996, # turn off in 2004
    state == "massachusetts" ~ 1992,
    state == "florida" ~ 1992,
    state == "kentucky" ~ 1998,
    state == "louisiana" ~ 2012,
    state == "mississippi" ~ 2011,
    state == "north dakota" ~ 2014,
    state == "california" ~ 1996, # could be 1996 or 1997
    state == "colorado" ~ 1996, # weird
    state == "district of columbia" ~ 1995,
    state == "kansas" ~ 1997,
    state == "missouri" ~ 1996,
    state == "new york" ~ 1995,
    state == "pennsylvania" ~ 1995,
    state == "south carolina" ~ 2007,
    state == "texas" ~ 1997,
    state == "virginia" ~ 1996,
    state == "west virginia" ~ 1997,
    state == "vermont" ~ 1997, # turn off in 2001
    
    ## alwayas treated
    state == "utah" ~ 1991, # weird
    state == "maryland" ~ 1991,
    state == "michigan" ~ 1991,
    state == "illinois" ~ 1991, ## weird
    state == "minnesota" ~ 1991,
    state == "ohio" ~ 1991,
    state == "wisconsin" ~ 1991
    
  ))

# remove always treated
# Create variable for center time for the treated groups
# Create binary treatment variable
dat <- main_data %>%
  filter(category != "always treated") %>% 
  filter(!(state %in% c("connecticut", "oklahoma", "vermont"))) %>% 
  mutate(center_time = ifelse(category %in% c("clean treated", "gradually treated"),
                              year - treatment_year,
                              0)) %>%
  dummy_cols(select_columns = "center_time") %>%
  mutate(treated = case_when(
    state %in% c(clean_treated_states, gradually_treated_states) & 
      year >= treatment_year ~ 1,
    state %in% c(clean_treated_states, gradually_treated_states) & 
      year < treatment_year ~ 0,
    state %in% never_treated_states ~ 0,
  ))

# Initialize results dataframe
results <- data.frame(state = character(), year = numeric(), gap = numeric())

treated_states <- c(clean_treated_states, gradually_treated_states)

dat <- dat %>%
  mutate(state_id = as.numeric(factor(state))) %>%
  rename(total_medicaid = `total medicaid (mt + at)`)

dat <- dat %>%
  mutate(log_total_spend = log(total_medicaid))

data <- dat #%>%
  # select(state, 
  #        year,
  #        pct_in_comp_mco,
  #        total_medicaid,
  #        log_total_spend,
  #        all_medicaid_spending_per_cap,
  #        log_all_medicaid_spending_per_cap, 
  #        treatment_year, 
  #        treated)
```

### Implementation for DiD, SC, Synth. DiD, Generate plots for different outcome variables

```{r}
# Get vector of cohort years
cohorts <- sort(unique(dat$treatment_year))
cohorts <- cohorts[!is.infinite(cohorts)]

# Initialize a list to store results
results <- list()

#' Function that implements DiD, SC, and Synth. DiD and plots outcomes
#' @param data panel data with state-year as units
#' @param outcome_var dependent variable we want to measure
#' @param cohorts vector of treatment years present throughout the data
run_synthdid <- function(data, outcome_var, cohorts) {
  
  outcome_labels <- c(
    pct_in_comp_mco = "Percent in Comp. MCO",
    total_medicaid = "Total Medicaid Spending",
    log_total_spend = "Log(Total Medicaid Spending)",
    all_medicaid_spending_per_cap = "Total Medicaid Spending per Capita",
    log_all_medicaid_spending_per_cap = "Log(Total Medicaid Spending per Capita)"
  )
  
  outcome_label <- outcome_labels[[outcome_var]]
  
  # Loop through each cohort
  for (cohort_year in cohorts) {

    tryCatch({
      # Subset data for the current cohort
      cohort_data <- data %>%
        filter(treatment_year == cohort_year | is.infinite(treatment_year))
    
      # Reshape the cohort data to wide format
      Y <- cohort_data %>%
        select(state, year, !!sym(outcome_var)) %>%
        pivot_wider(names_from = year, 
                    values_from = !!sym(outcome_var)) %>%
        column_to_rownames("state") %>%
        as.matrix()
      
      # Extract treatment timing for the cohort
      treatment_timing <- cohort_data %>%
        group_by(state) %>%
        summarize(treatment_year = unique(treatment_year)) %>%
        pull(treatment_year)
      
      # Number of control units (N0)
      N0 <- sum(treatment_timing == Inf)
      
      # Number of pre-treatment periods (T0)
      T0 <- cohort_year - min(cohort_data$year)
      
      # Check if Y has valid dimensions
      if (nrow(Y) == 0 || ncol(Y) == 0) {
        stop("Y has invalid dimensions. Skipping cohort year ", cohort_year)
      }
      
      # Estimate the treatment effect using synthdid
      tau.hat <- synthdid_estimate(Y, N0, T0)
      
      # Define estimators
      estimators <- list(did = did_estimate,
                         sc = sc_estimate,
                         sdid = synthdid_estimate)
      
      # Apply estimators
      estimates <- lapply(estimators, function(estimator) {estimator(Y, N0, T0)})
      
      # Generate the plot
      plot <- synthdid_plot(estimates[1:3],
                            control.name = 'control',
                            treated.name = "treated",  # Use the treated unit's name
                            facet.vertical = FALSE,
                            lambda.comparable = TRUE,
                            se.method = 'none',
                            trajectory.linetype = 1,
                            line.width = .75,
                            effect.curvature = -.4,
                            trajectory.alpha = .7,
                            effect.alpha = .7,
                            diagram.alpha = 1,
                            onset.alpha = .7) +
        labs(title = paste0("Estimators - ", outcome_label),
             subtitle = paste0("Treatment Year = ", cohort_year),
             x = "Year",
             y = outcome_var)
      
      print(plot)
      
      # Print a success message
      message("Plot saved for cohort year ", cohort_year)
      
    }, error = function(e) {
      # Print an error message and skip the cohort year
      message("Error in cohort year ", cohort_year, ": ", e$message)
    })
  }
}
```

### Percent in Comprehensive Managed Care 

```{r}
run_synthdid(data, "pct_in_comp_mco", cohorts)
```

### Total Medicaid Spending

```{r}
run_synthdid(data, "total_medicaid", cohorts)
```

### Log(Total Medicaid Spending)

```{r}
run_synthdid(data, "log_total_spend", cohorts)
```

### Total Medicaid Spending per Capita

```{r}
run_synthdid(data, "all_medicaid_spending_per_cap", cohorts)
```

### Log(Total Medicaid Spending per Capita)

```{r}
run_synthdid(data, "log_all_medicaid_spending_per_cap", cohorts)
```


### TWFE Treatment Effect by Cohort (cohorts based off 5-10 year intervals)

```{r}
# Define 5 and 10 year interval cohorts based on treatment years
data_cohorts <- data %>%
  mutate(cohort_5_interval = case_when(
    treatment_year >= 1991 & treatment_year <= 1995 ~ "1991-1995",
    treatment_year >= 1996 & treatment_year <= 2000 ~ "1996-2000",
    treatment_year >= 2001 & treatment_year <= 2005 ~ "2001-2005",
    treatment_year >= 2006 & treatment_year <= 2010 ~ "2006-2010",
    treatment_year >= 2011 & treatment_year <= 2015 ~ "2011-2015",
    treatment_year >= 2016 & treatment_year <= 2022 ~ "2016-2022",
    TRUE ~ "never-treated"
  )) %>%
  mutate(cohort_10_interval = case_when(
    treatment_year >= 1991 & treatment_year <= 2000 ~ "1991-2000",
    treatment_year >= 2001 & treatment_year <= 2010 ~ "2001-2010",
    treatment_year >= 2011 & treatment_year <= 2022 ~ "2011-2022",
    TRUE ~ "never-treated"
  ))
```

```{r, warning=FALSE}

# Vector of relative time variables
keepvars <- c(paste0("`center_time_-", 10:2, "`"),  
              paste0("center_time_", 0:10))

prep_es_10 <- function(mod){
  mod_2 <- tibble(
    estimate = mod$coefficients,
    term1 = rownames(mod$coefficients),
    se = mod$se,
    pval = mod$pval
  )
  
  # Filter coefficients for relative time leads and lags
  es <- mod_2 %>% 
    filter(term1 %in% keepvars) %>% 
    mutate(t = c(-10:-2, 0:10)) %>% 
    select(t, estimate, se, pval)
  
  # Add a row for t = -1 (reference period)
  es <- rbind(es, c(-1, 0, 0, 0))
  
  # Add confidence intervals
  es <- es %>% 
    mutate(lower = estimate - 1.96 * se,
           upper = estimate + 1.96 * se)
  
  return(es)
}

prep_es_trend_10 <- function(mod){
  mod_2 <- tibble(
    estimate = mod$coefficients,
    term1 = rownames(mod$coefficients),
    se = mod$se,
    pval = mod$pval
  )
  
  es <- mod_2 %>% 
    filter(term1 %in% keepvars) %>% 
    mutate(t = c(0:10)) %>% 
    select(t, estimate, se, pval)
  es <- rbind(es, c(-1, 0, 0, 0))
  es <- es %>% 
    mutate(lower = estimate - 1.96 * se,
           upper = estimate + 1.96 * se,
           star = ifelse(pval <= 0.001, "***", 
                         ifelse(pval<=0.01,"**", 
                                ifelse(pval<=0.05, "*", ""))),
           coef_star = paste0(round(estimate,2), star, sep =""))
  return(es)
}

#' Plot 10-year event study plot with data filtered by interval cohort
#' @param data panel data
#' @param outcome outcome variable (numeric)
#' @param outcome_name name of the outcome variable (character)
#' @param cohort_var name of the interval variable (character)
#' @param cohort_interval range of years (cohort) we want to filter for (character)
did_graph_trend_10 <- function(data, outcome, outcome_name, cohort_var, cohort_interval){
  p <- list()
  
  cohort_data <- data %>%
    filter(!!sym(cohort_var) == cohort_interval)
  
  # Normal event study 
  formula_str1 <- paste0(
    outcome, " ~ ",
    "`center_time_-10` + `center_time_-9` + ",
    "`center_time_-8` + `center_time_-7` + `center_time_-6` + `center_time_-5` + ",
    "`center_time_-4` + `center_time_-3` + `center_time_-2` + `center_time_0` + ",
    "`center_time_1` + `center_time_2` + `center_time_3` + `center_time_4` + ",
    "`center_time_5` + `center_time_6` + `center_time_7` + `center_time_8` + ",
    "`center_time_9` + `center_time_10` | ",
    "as.factor(state) + as.character(year) ",
    sep = ""
  )
  formula1 <- as.formula(formula_str1)
  mod_d <- lfe::felm(formula1, 
                     data = subset(cohort_data, center_time >= -10 & center_time <= 10),
                     exactDOF = TRUE)
  es_d <- prep_es_10(mod_d)
  
  es_d <- es_d %>% 
    mutate(sig = ifelse((lower > 0 | upper < 0), 1, 0))
  
  # Pre-trend line
  pre_trend <- es_d %>% filter(t < 0) 
  pre_trend_fit <- lm(estimate ~ t, data = pre_trend)
  predicted_df <- data.frame(
    t = seq(-10, 10, by = 0.1),
    estimate = predict(pre_trend_fit, newdata = data.frame(t = seq(-10, 10, by = 0.1)))
  )
  
  ## estimate difference
  formula_str2 <- paste0(
    outcome, " ~ ",
    "`center_time_0` + ",
    "`center_time_1` + `center_time_2` + `center_time_3` + `center_time_4` + ",
    "`center_time_5` + `center_time_6` + `center_time_7` + `center_time_8` + ",
    "`center_time_9` + `center_time_10` + ",
    "center_time | ",
    "as.factor(state) + as.character(year) ",
    sep = ""
  )
  formula2 <- as.formula(formula_str2)
  mod_d <- lfe::felm(formula2, 
                     data = subset(cohort_data, center_time >= -10 & center_time <= 10),
                     exactDOF = TRUE)
  es_d2 <- prep_es_trend_10(mod_d)
  
  es_d2 <- es_d2 %>% 
    mutate(sig = ifelse((lower > 0 | upper < 0), 1, 0))
  
  # Event study plot
  p1 <- ggplot(data = es_d, aes(x = t, y = estimate, group = 1))+
    geom_point(size= 3, color = "gray26")+
    geom_errorbar(aes(ymin = lower, ymax = upper), 
                  width=.1, 
                  linewidth = 0.8, 
                  color = "gray26") +
    geom_hline(yintercept = 0, 
               linetype = "dashed", 
               linewidth = 1,
               color = "firebrick4")+
    scale_x_continuous(breaks = round(seq(-10, 10, by = 1),1),
                       limits = c(-10.5, 10.5))+
    # scale_y_continuous(breaks = round(seq(-0.2, 0.2, by = 0.1), 1),
    #                  limits = c(-0.2, 0.2))+
    labs(x = "Relative Time", y = "Estimate",
         title = paste0(outcome_name, " - ", cohort_interval))+
    theme(plot.title = element_text(hjust = 0.5, size = 15),
          legend.position = "none")+
    geom_text(data = es_d2 %>% filter(t >= 0 & t <= 10), 
              aes(x = t, y = 0.5*max(es_d2$upper), label = coef_star, angle = 45),
              color = "blue", size = 4, vjust = -0.3)+
    geom_line(data = predicted_df, aes(x = t, y = estimate), 
              color = "blue", linetype = "dashed", linewidth = 1.2)
  # annotate("text", x = 8, y = text_pos, label = comb_est, size = 5)
  
  p2 <- ggplot(data = es_d2, aes(x = t, y = estimate)) +
    geom_point(size = 3, color = "black") +  # Black dots for estimates
    geom_errorbar(aes(ymin = lower, ymax = upper), 
                  width = 0.2, 
                  linewidth = 0.8, 
                  color = "black") +  # Error bars
    geom_line(color = "black", linewidth = 1) +  # Line connecting estimates
    geom_hline(yintercept = 0, linetype = "dashed", color = "firebrick4", linewidth = 1) +  # Reference line at y = 0
    scale_x_continuous(breaks = seq(-20, 20, by = 1)) +
    # scale_y_continuous(breaks = seq(-0.5,1,0.1),
    #                    limits = c(-0.5, 1.1))+
    labs(x = "Relative Time", 
         y = "Estimate", 
         title = paste0(outcome_name, " - ", cohort_interval)) +
    theme(plot.title = element_text(hjust = 0.5, size = 15),
          legend.position="none")
  p2
  
  p[[1]] <- p1
  p[[2]] <- p2
  return(p)
}
```

```{r, warning=FALSE}

# Define treatment cohorts
assign_cohort_5 <- function(treatment_year) {
  case_when(
    is.na(treatment_year) ~ "never-treated",
    treatment_year >= 1996 & treatment_year <= 2000 ~ "1996-2000",
    treatment_year >= 1991 & treatment_year <= 1995 ~ "1991-1995",
    treatment_year >= 2006 & treatment_year <= 2010 ~ "2006-2010",
    treatment_year >= 2016 & treatment_year <= 2022 ~ "2016-2022",
    treatment_year >= 2011 & treatment_year <= 2015 ~ "2011-2015",
    TRUE ~ "never-treated"  # Default fallback if none of the above match
  )
}

# Construct stacked data
# For each treatment year, construct control without treatment within 10/20 years
collect_10 <- list()
collect_20 <- list()

for(i in unique(data_cohorts$treatment_year[data_cohorts$treatment_year != Inf])){
  
  # Get treated state
  treated_state <- data_cohorts %>%
    filter(treatment_year == i) %>% 
    mutate(treatment_year_group = i) %>%
    mutate(cohort_5_interval = assign_cohort_5(treatment_year_group)) %>%
    select(state, year, center_time, treated, total_medicaid,
           log_all_medicaid_spending_per_cap, all_medicaid_spending_per_cap,
           pct_in_comp_mco, treatment_year, treatment_year_group, cohort_5_interval)
  
  max_year <- max(treated_state$year)
  
  # Get control states within a 10 year (pre and post) from treatment year
  control_state_10 <- data_cohorts %>% 
    filter(treatment_year > i + 10,
           year <= i + 10, year >= i - 10) %>% 
    mutate(treatment_year_group = i,
           center_time = 0,
           treated = 0,
           cohort_5_interval = assign_cohort_5(treatment_year_group)) %>% 
    select(state, year, center_time, treated, total_medicaid,
           log_all_medicaid_spending_per_cap, all_medicaid_spending_per_cap,
           pct_in_comp_mco, treatment_year, treatment_year_group, cohort_5_interval)
  
  control_state_20 <- data_cohorts %>% 
    filter(treatment_year > i + 20, 
           year <= i + 20, year >= i - 20) %>% 
    mutate(treatment_year_group = i,
           center_time = 0,
           treated = 0,
           cohort_5_interval = assign_cohort_5(treatment_year_group)) %>%
    select(state, year, center_time, treated, total_medicaid,
           log_all_medicaid_spending_per_cap, all_medicaid_spending_per_cap,
           pct_in_comp_mco, treatment_year, treatment_year_group, cohort_5_interval)
  
  collect_10[[length(collect_10)+1]] <- rbind(treated_state, control_state_10)
  collect_20[[length(collect_20)+1]] <- rbind(treated_state, control_state_20)
}

# Collapse into one dataframe
dat_10 <- do.call(rbind, collect_10)
dat_20 <- do.call(rbind, collect_20)

dat_10 <- dat_10 %>% dummy_cols(select_columns = "center_time")
dat_20 <- dat_20 %>% dummy_cols(select_columns = "center_time")

# DID - 10 period
dat <- dat_10
dat <- dat %>%
  mutate(log_total_spend = log(total_medicaid))

```


### Plots for 5 year interval cohorts

```{r, warning=FALSE}

cohorts <- c("1991-1995", "1996-2000", "2006-2010", "2011-2015", "2016-2022")

outcomes <- list(
  pct_in_comp_mco = "Prop. Comp MCO Enroll",
  log_total_spend = "Log(Total Medicaid Spending)",
  log_all_medicaid_spending_per_cap = "Log(Total Medicaid Spending per Capita)"
)


# Initialize an empty list to store the plots
plot_list <- list()

# Loop through each outcome
for (outcome_name in names(outcomes)) {
  outcome_label <- outcomes[[outcome_name]]
  
  # Loop through each cohort
  for (cohort in cohorts) {
    # Generate the plot
    p <- did_graph_trend_10(dat, outcome_name, outcome_label, "cohort_5_interval", cohort)
  
    # Store the plot in the list
    plot_list[[paste(outcome_name, cohort, sep = "_")]] <- p
  }
  
  outcome_plots <- plot_list[grep(outcome_name, names(plot_list))]
  print(outcome_plots)
}
```

```{r}
# Define treatment cohorts
assign_cohort_10 <- function(treatment_year) {
  case_when(
    treatment_year >= 1991 & treatment_year <= 2000 ~ "1991-2000",
    treatment_year >= 2001 & treatment_year <= 2010 ~ "2001-2010",
    treatment_year >= 2011 & treatment_year <= 2022 ~ "2011-2022",
    TRUE ~ "never-treated"  # Default fallback if none of the above match
  )
}

# Construct stacked data
# For each treatment year, construct control without treatment within 10/20 years
collect_10 <- list()
collect_20 <- list()

for(i in unique(data_cohorts$treatment_year[data_cohorts$treatment_year != Inf])){
  
  # Get treated state
  treated_state <- data_cohorts %>%
    filter(treatment_year == i) %>% 
    mutate(treatment_year_group = i) %>%
    mutate(cohort_10_interval = assign_cohort_10(treatment_year_group)) %>%
    select(state, year, center_time, treated, total_medicaid,
           log_all_medicaid_spending_per_cap, all_medicaid_spending_per_cap,
           pct_in_comp_mco, treatment_year, treatment_year_group, cohort_10_interval)
  
  max_year <- max(treated_state$year)
  
  # Get control states within a 10 year (pre and post) from treatment year
  control_state_10 <- data_cohorts %>% 
    filter(treatment_year > i + 10,
           year <= i + 10, year >= i - 10) %>% 
    mutate(treatment_year_group = i,
           center_time = 0,
           treated = 0,
           cohort_10_interval = assign_cohort_10(treatment_year_group)) %>% 
    select(state, year, center_time, treated, total_medicaid,
           log_all_medicaid_spending_per_cap, all_medicaid_spending_per_cap,
           pct_in_comp_mco, treatment_year, treatment_year_group, cohort_10_interval)
  
  control_state_20 <- data_cohorts %>% 
    filter(treatment_year > i + 20, 
           year <= i + 20, year >= i - 20) %>% 
    mutate(treatment_year_group = i,
           center_time = 0,
           treated = 0,
           cohort_10_interval = assign_cohort_10(treatment_year_group)) %>%
    select(state, year, center_time, treated, total_medicaid,
           log_all_medicaid_spending_per_cap, all_medicaid_spending_per_cap,
           pct_in_comp_mco, treatment_year, treatment_year_group, cohort_10_interval)
  
  collect_10[[length(collect_10)+1]] <- rbind(treated_state, control_state_10)
  collect_20[[length(collect_20)+1]] <- rbind(treated_state, control_state_20)
}

dat_10 <- do.call(rbind, collect_10)
dat_20 <- do.call(rbind, collect_20)

dat_10 <- dat_10 %>% dummy_cols(select_columns = "center_time")
dat_20 <- dat_20 %>% dummy_cols(select_columns = "center_time")

# DID - 10 period
dat <- dat_10
dat <- dat %>%
  mutate(log_total_spend = log(total_medicaid))
```


### Plots for 10 year interval cohorts

```{r, warning=FALSE}

cohorts2 <- c("1991-2000", "2001-2010", "2011-2022")

outcomes <- list(
  pct_in_comp_mco = "Prop. Comp MCO Enroll",
  log_total_spend = "Log(Total Medicaid Spending)",
  log_all_medicaid_spending_per_cap = "Log(Total Medicaid Spending per Capita)"
)


# Initialize an empty list to store the plots
plot_list <- list()

# Loop through each outcome
for (outcome_name in names(outcomes)) {
  outcome_label <- outcomes[[outcome_name]]
  
  # Loop through each cohort
  for (cohort in cohorts2) {
    # Generate the plot
    p <- did_graph_trend_10(dat, outcome_name, outcome_label, "cohort_10_interval", cohort)
  
    # Store the plot in the list
    plot_list[[paste(outcome_name, cohort, sep = "_")]] <- p
  }
  
  outcome_plots <- plot_list[grep(outcome_name, names(plot_list))]
  print(outcome_plots)
}
```


### De Chaisemartin and D'Haultfoeuille (2020) (Callaway-Sant'anna)

### Percent in Comprehensive MCO

```{r, echo = FALSE, warning = FALSE}
result <- att_gt(
  yname = "pct_in_comp_mco",
  tname = "year",
  idname = "state_id",
  gname = "treatment_year",
  control_group = "nevertreated",
  data = data
)

agg_results <- aggte(result, type = "dynamic")

p1 <- ggdid(agg_results) + 
  labs(title = "Percent in Comprehensive MCO Enrollment")

```

### Total Medicaid Enrollment

```{r, echo = FALSE, warning = FALSE}
result <- att_gt(
  yname = "total_med_enr",
  tname = "year",
  idname = "state_id",
  gname = "treatment_year",
  control_group = "nevertreated",
  data = data
)

agg_results <- aggte(result, type = "dynamic")

ggdid(agg_results) + 
  labs(title = "Total Medicaid Enrollment")
```

### Total Medicaid Spending

```{r, echo = FALSE, warning = FALSE}
result <- att_gt(
  yname = "total_medicaid",
  tname = "year",
  idname = "state_id",
  gname = "treatment_year",
  control_group = "nevertreated",
  data = data
)

agg_results <- aggte(result, type = "dynamic")

ggdid(agg_results) + 
  labs(title = "Total Medicaid Spending")
```

### Log(Total Medicaid Spending)

```{r, echo = FALSE, warning = FALSE}
result <- att_gt(
  yname = "log_total_spend",
  tname = "year",
  idname = "state_id",
  gname = "treatment_year",
  control_group = "nevertreated",
  data = data
)

agg_results <- aggte(result, type = "dynamic")

ggdid(agg_results) + 
  labs(title = "Log(Total Medicaid Spending)")

```

### Total Medicaid Spending per Capita

```{r, echo = FALSE, warning = FALSE}
result <- att_gt(
  yname = "all_medicaid_spending_per_cap",
  tname = "year",
  idname = "state_id",
  gname = "treatment_year",
  control_group = "nevertreated",
  data = data
)

agg_results <- aggte(result, type = "dynamic")

ggdid(agg_results) + 
  labs(title = "Total Medicaid Spending per Capita")

```

### Log(Total Medicaid Spending per Capita)

```{r, echo = FALSE, warning = FALSE}
result <- att_gt(
  yname = "log_all_medicaid_spending_per_cap",
  tname = "year",
  idname = "state_id",
  gname = "treatment_year",
  control_group = "nevertreated",
  data = data
)

agg_results <- aggte(result, type = "dynamic")

ggdid(agg_results) + 
  labs(title = "Log(Total Medicaid Spending per Capita)")

```










